---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# SurveyExactDataImporter

The goal of SurveyExactDataImporter is to ...

## Installation

You can install the released version of SurveyExactDataImporter from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("SurveyExactDataImporter")
```

## How to export data in the proper format from SurveyExact

1. Open the questionaire in SurveyExact
2. Find the "Dataset" in the sidepanel to the right
3. Under "Nyeste data" - "Eksporter datasæt" - "Excel XML"
4. Check all boxes except "Behold linjeskift" in the dialog that appears
5. Click on "Hent fil"


## Example

Load example dataset.

```{r}
data <- load('../testdata/dataset_1172477_20170127_356700854610526206.xlsx')

get_variable_name(data, 's_73')
get_variable_name_category(data, 's_73')
get_variable_name_subcategory(data, 's_73')

ggplot(data$data) + 
  geom_bar(aes(s_73)) + 
  scale_x_discrete(drop=FALSE) +
  coord_flip() + 
  labs(subtitle = get_variable_name(data, 's_73'), 
       x = "")
```
