---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# SurveyExactDataImporter

The goal of SurveyExactDataImporter is to simplify loading of data from the online questionaire system SurveyExact.

## Installation

You can install the development version of SurveyExactDataImporter from [github](https://github.com/henrikmidtiby/SurveyExactDataImporter) with:

``` r
library(devtools)
install_github("henrikmidtiby/SurveyExactDataImporter")
```

## How to export data in the proper format from SurveyExact

1. Open the questionaire in SurveyExact
2. Find the "Dataset" in the sidepanel to the right
3. Under "Nyeste data" - "Eksporter datasæt" - "Excel XML"
4. Check all boxes except "Behold linjeskift" in the dialog that appears
5. Click on "Hent fil"


## Example

Load libraries

```{r}
library(SurveyExactDataImporter)
library(ggplot2)
```

Load example dataset.

```{r}
data <- load_survey_exact_data("data/dataset_1488637_20180512_1825827966544069436.xlsx")
```

Show a summary of the imported data. 
Note that the factor levels are sorted as specified in SurveyExact and not 
alphabetically as otherwise is the standard approach (what else to to when it is not specified ...).
```{r}
summary(data$data)
```


Extract information about a certain element in the questionaire.

```{r}
get_variable_name(data, 's_6')
get_variable_name_category(data, 's_6')
get_variable_name_subcategory(data, 's_6')
```

Show distribution of answers to a single question (s_6).
```{r}
ggplot(data$data) + 
  geom_bar(aes(s_6)) + 
  scale_x_discrete(drop=FALSE) +
  coord_flip() + 
  labs(subtitle = get_variable_name(data, 's_6'), 
       x = "")
```


Make a scatter plot of answers to two questions (s_6 and s_7).
```{r}
ggplot(data$data) + 
  geom_count(aes(s_6, s_7)) + 
  scale_x_discrete(drop=FALSE) +
  scale_y_discrete(drop=FALSE) +
  coord_flip() +
  labs(title = get_variable_name_category(data, 's_6'), 
       x = get_variable_name_subcategory(data, 's_6'), 
       y = get_variable_name_subcategory(data, 's_7')) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1), 
        axis.text.y = element_text(angle = 30, hjust = 1, vjust = 1))
```


